Results from Primary Coding

### 2023-08-31 analysis/practiceCoding_AW.Rmd
Replaced primary with FINAL coding

#Prelim results and visualisations for d_journals using Primary coding data only

@@

d_primaryONLY <- d_journals %>%
  filter(coder_id == "AW" | coder_id == "NM") %>% #keeps only entries with primary coder initials from main data tibble d_journals
  filter(journal_empirical == "Yes") %>%          #removes ineligible journals (not empirical)
  group_by(journal) %>%
  distinct(journal, .keep_all = TRUE)             #keeps only distinct journal entries

 table(d_primaryONLY$sampleID, d_primaryONLY$anyPPC)

 table(d_primaryONLY$sampleID)
```

@@

# Removes journals that do not offer any PPC 
 d_PPConly <- d_primaryONLY %>%
   filter(anyPPC == "YES")

@@

#All 14 duplicated (both sample) journals had consistent COPE status, join with main data tibble:
d_cope <- left_join(d_journals, dj_cope, by = 'journal')

@@

>>>>

#Prelim results and visualisations for d_journals using FINAL coding data only

@@

d_FINAL <- d_journals %>%
  filter(coder_id == "FINAL (TEH)") %>% #keeps only FINAL coded by TEH
  filter(journal_empirical == "Yes") %>%          #removes ineligible journals (not empirical)
  group_by(journal) %>%
#  distinct(journal, .keep_all = TRUE) %>%        #keeps only distinct journal entries
    mutate(anyPPC = case_when(
    anyPPC == 'Unclear' | anyPPC == 'UNSURE' | anyPPC == 'Unclear type' ~ 'UNCLEAR',
    anyPPC == 'NO (explicit statement that PPC is not accepted)' | anyPPC == 'NO (there are no PPC options)' ~ 'NO',
    TRUE ~ anyPPC
    ))

 table(d_FINAL$sampleID, d_FINAL$anyPPC)

 table(d_FINAL$sampleID)
```

# Calculate CIs for YES 
```{r}
library(binom)

# Prominent Sample data
prominentSuccess <- 47
randomSuccess <- 29
totalSuccess <- 72

sample_size <- 100
totalSample <- 189
confidence_level <- 0.95

# Calculate the Wilson confidence interval
ci_prominent <- binom.confint(prominentSuccess, sample_size, method = "wilson", conf.level = confidence_level)
ci_random <- binom.confint(randomSuccess, sample_size, method = "wilson", conf.level = confidence_level)
ci_total <- binom.confint(totalSuccess, totalSample, method = "wilson", conf.level = confidence_level)

# Print the confidence interval
print(ci_prominent)
print(ci_random)
print(ci_total)
```

@@

# Removes journals that do not offer any PPC 
 d_PPConly <- d_FINAL %>%
   filter(anyPPC == "YES")

@@

#All 14 duplicated (both sample) journals had consistent COPE status, remove duplicates
dj_cope <- distinct(dj_cope, journal, .keep_all = T)

#join with main data tibble:
d_FINAL <- left_join(d_FINAL, dj_cope, by = 'journal')

@@

# Bar graph of PPC by COPE

```{r}

# Create bar plot
d_FINAL %>%  
  ggplot() +
geom_bar(
  mapping = aes(x=anyPPC, fill = COPE),
  stat = "count",
  position = "stack",
  colour = "black",
  just = 0.5,
  width = 0.7,
  na.rm = FALSE,
  orientation = NA,
  show.legend = TRUE,
  inherit.aes = TRUE
) +
  theme_bw() +
  scale_fill_brewer(palette = "Blues")
 # facet_wrap(~field) +
  labs(title = "Journal PPC Acceptance by COPE membership", x = "Accepts PPC", y = "Count")
```
